Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-11 ms.tex
showing results of long sub320 multi exposure test

\subsection{Noise floor}

>>>>

\subsection{Long multi-exposure Test}
\textbf{\textcolor{red}{Show exposure boundaries}}

\begin{figure*}
{\gridline{\fig{individual_azlab06_sub320_multi_exp.pdf}{0.48\textwidth}{AZLab06 Long Multi-Exposure Time series}
\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
\caption{We strung together 4 long exposures to create an extended time series.
There are no obvious transients or exponentials at the exposure boundaries.
As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.}\label{fig:AZlab06LongMultiExp}
\end{figure*}

\clearpage
\subsection{Noise floor}
